A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-31 1_intro.tex
Tim: redo related work

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} is employing a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size, which influences mechanical and surface properties of the part~\cite{N.Turner2014,ahn2002anisotropic}.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.
Therefore, a narrower range of widths is desirable.

>>>>

The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} is employing a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.
Therefore, a narrower range of widths is desirable.

### 2019-08-31 2_related_work.tex
Tim: redo related work

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
The nozzle is then instructed to move along the path while extruding material.
The deposited material covers the path with a certain width.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}~\cite{Livesu2017CGF}.
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
This is sometimes called dense infill~\cite{Livesu2017CGF}.

% criteria for toolpath generation
Toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object.
There are a few desirable properties for the toolpath.
First, the path shall be as continuous as possible.
A discontinuous path requires to stop and restart material extrusion.
For certain material such as TPU, this could lead to material defects~\cite{KUIPERS2019CAD}.
Furthermore, a smooth path is often preferred.
Sharp turns require to slow down the movement of the nozzle, and this consequently prolongs the printing process.
Second, the path, extended with a certain width, ideally shall cover the bounded region without voids or gaps --  underfilling, and no overlap -- overfilling. 
An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
Our method is primarily concerned with minimizing under- and overfill within slices, i.e. horizontal cross-sections.

% basic toolpath strategies and their variations
Direction parallel and contour-parallel are two basic toolpath strategies.
Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
Contour-parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
\citeauthor{steuben2016implicit} presented implicit slicing and made an interpretation of 2D contour computing as evaluating intersections in 3D~\cite{steuben2016implicit}.
A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour~\cite{Zhao2016}. 
Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
One of the problems with contour-parallel toolpath is that it tends to leave gaps within the slices (\cref{intro_wedge} top).
This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are a few contour-parallel curves, while in the interior there is a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour-parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting variation of width in the central is pronounced (\cref{intro_wedge} middle).
In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).

>>>>

% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
%Toolpath generation for deposition based additive manufacturing consists in generating geometric paths which the nozzle follow during printing.
%Extrusion toolpaths are generated within the planar contour of a layer at the intersection of a horizontal plane and a 3D solid object.
Toolpath generation consists in generating a path in the a planar contour, representing the intersection of a plane and a 3D solid object.
The nozzle is then instructed to move along the path while extruding material.
Sites along the toolpath are assigned several properties such as movement speed, but for this paper we will focus on the assigned width of the extruded bead.
Toolpath generation is an integral part of process planning for 3D printing.
For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}~\cite{Livesu2017CGF}.
For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
This is sometimes called `dense infill'~\cite{Livesu2017CGF}.

% criteria for toolpath generation
The toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object~\cite{N.Turner2014,ahn2002anisotropic}.
FDM calls for toolpaths with several desirable properties.
First, the extrusion path should be as continuous as possible.
A discontinuous path requires to stop and restart material extrusion.
For certain materials such as TPU, this could lead to printing defects or even print failure~\cite{KUIPERS2019CAD}.
Second, the toolpath is preferred to be smooth.
Sharp turns require to slow down the movement of the nozzle, and this consequently prolongs the printing process.
Third, the extruded path should cover a the region of the contour without gaps.
Such underfill negatively influences the mechanical performance of the parts.
Fourth, the extrusion paths should not overlap with one another.
Such overfill causes a pressure build up in the mechanical system, which leads to overextrusion in further paths and in extreme cases cause print failure~\cite{KUIPERS2019CAD}.
An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
Our method is primarily concerned with minimizing under- and overfill within horizontal cross-sections.

% basic toolpath strategies and their variations
Two basic strategies for dense toolpath generation are direction-parallel and contour-parallel.
Direction-parallel (or zig-zag) toolpaths fill an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
These parallel segments are linked together at one of their extremities, to avoid discontinuous extrusion.
Contour-parallel toolpaths typically consists of a set of equally spaced offsets from the slice boundary outline polygons.
\citeauthor{steuben2016implicit} presented a method for generating sparse infill toolpaths based on the isocontours of surface plots of some variable generated on each 2D contour~\cite{steuben2016implicit}.
In order to increase the continuity of contour-parallel toolpaths, a strategy to connect dense toolpaths into spirals was introduced by \citeauthor{Zhao2016}~\cite{Zhao2016} and later extended to also connect a mixture of dense and sparse toolpaths together~\cite{KUIPERS2019CAD}.
\citeauthor{Jin2017RCIM} discusses several approaches for connecting direction-parallel and contour-parallel toolpaths into continuous paths~\cite{Jin2017RCIM}.
Spiral toolpaths have also been applied to (CNC) machining~\cite{Held2009,Huang2017}.
One of the problems with contour-parallel toolpath is that it tends to leave gaps between the toolpaths (see \cref{intro_wedge_uniform}).
This is due to the fact that the diameter of the part is not exact multiple of the (cosntant) deposition width in those regions.
To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
Close to the slice boundary, there are several contour-parallel curves, while in the interior is filled using a zig-zag pattern.
For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
%Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
\citeauthor{kao1998optimal} propose smooth adaptive toolpaths based on the medial axis skeleton of the boundary contour~\cite{kao1998optimal}.
Their approach handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
However, this extension inherits a problem in the original method:
from any point in the skeleton to the boundary, the number of toolpaths is constant.
Since the distance may vary considerably for shapes with both large and small features, this strategy leads to a toolpath with widths that may differ by a factor beyond $3$, which is impossible for some FDM systems.
\citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting variation of width in the center is still up to a factor of $2$ (see \cref{intro_wedge_centered}).
In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurence of extreme deviations in width (see \cref{intro_wedge_distributed}).

### 2019-08-31 8_discussion.tex
Tim: redo related work

\subsection{Discussion on implications}
Note that the current industry standard in FDM printing employs little to no bead width variation.
Properly performing bead width variation calls for adaptations and developments in printers and firmware.
In the beading schemes we set a transition length of $t(n) = w^*$.
That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
Varying the movement speed can be utilised to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath.
Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) outperforms Bowden style FDM printers in terms of dynamic flow changes,
but still requires some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
We expect that developments in printing hardware and firmware will address these challenges in the future.

>>>>

\subsection{Discussion on implications}
Note that the current industry standard in FDM printing employs little to no bead width variation.
Properly performing bead width variation calls for adaptations and developments in printers and firmware.
In the beading schemes we set a transition length of $t(n) = w^*$.
That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
Varying the movement speed can be utilised to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) can control the flow more dynamicaly then FDM printers where the material is fed through a Bowden tube from a feeder mounted on the frame.
Still direct drive printers require some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
We expect that developments in printing hardware and firmware will address these challenges in the future.
